---
title: "Case Study 04"
author: Jeongwon Lee
date: Sep 24, 2024
output: github_document
---

## Join tables
# What is the full name of the destination airport farthest from any of the NYC airports in the flights table?

Sometime, we need to integrate and connect multiple tables to get what we want.
Then, we can use a join function which combines columns from one or more tables into a new table.

The full names of airport is stored in 'airport' table and we have flight information in 'flight' table.
Therefore, we can join them by their common columns, which *'dest'* and *'faa'*.

```{r}
# library
library(tidyverse)
library(nycflights13)

# Join two datasets using a common column
flights_joined <- left_join(flights, airports, by = c('dest' = 'faa'))

# View 5 random rows with only origin, destination, distance and name of airport columns
head(flights_joined[,c('origin', 'dest', 'distance', 'name')])
```

## Find data which meets our condition
# What is the full name of the destination airport farthest from any of the NYC airports in the flights table?

Once we joined the tables, we can find data which we want by filtering.

```{r}

farthest_airport <- flights_joined %>% filter(distance == max(distance)) %>% select(name) %>% distinct()
farthest_airport

```

## Plot the result
Let's visualize what we found.

```{r}
# US basemap
library(maps)
library(mapdata)

usa <- map_data('usa')

ggplot(data = usa, aes(x = long, y = lat)) + 
  geom_polygon() + 
  geom_point(data = flights_joined, aes(x = lon, y = lat, color = distance)) + 
  scale_color_gradient(low = "pink", high = "darkred") +
  coord_quickmap() +
  ggtitle("The flight distance from NY airport")

```
